---
title: "Content Based Recommendation Systems"
author: "Muthia"
date: "8/27/2020"
output: html_document
---

1. User Similarity (The User-Based Collaborative Filtering Approach) 

  
library(recommenderlab)
library(reshape2)
library(ggplot2)                       
library(data.table)
library(ggplot2)
library(pheatmap)


```{r}
path_name <- 'C:/Users/Aulia Muthia/Downloads/Riset Mandiri/IMDB-Dataset'

ratings = read.csv(paste0(path_name, '/ratings.csv'), stringsAsFactors = FALSE)
movies = read.csv(paste0(path_name, '/movies.csv'), stringsAsFactors = FALSE)
# create year column
movies = movies %>% mutate(year = as.integer(str_extract(title, "([[:digit:]]{4})")))
# limit to more recent movies
ratings = ratings %>% 
  left_join(movies, by = 'movieId') %>%
  select(userId, movieId, rating,  title)

ratings 
movies
```

1. User Similarity

# Pivot Movie Title on Userid
```{r}
user_ratings = ratings %>%
    pivot_wider(names_from = userId, values_from = rating)
head(user_ratings)
```

# Change Colnames on user_ratings table

```{r}
#subset user id only
user_id <- user_ratings %>% select(-movieId,-title)
head(user_id)

#subset title id only
movie_title <- user_ratings %>% select(title)
head(movie_title)

#change user id column name
cnames <- colnames(user_id) 

colnames(user_id) <- paste0("User", cnames)
head(user_id)

#merge user id column with movie id & title id
user_ratings <- cbind(movie_title[], user_id[])
head(user_ratings)
str(user_ratings)

#change to matrix
user_ratings_matrix <- as.matrix(user_ratings)
head(user_ratings_matrix)

#change NA to 0
user_ratings_matrix[is.na(user_ratings_matrix)] = 0
head(user_ratings_matrix)

#ratings only matrix 
#change NA to 0
ratings_only_matrix[is.na(ratings_only_matrix)] = 0
head(ratings_only_matrix)
```

#cor matrix

```{r}
user_correlation_matrix <- round(cor(ratings_only_matrix),2)
head(user_correlation_matrix)
```

#melt matrix

```{r}
melt_similar_user <- melt(user_correlation_matrix)
head(melt_similar_user)
```


#take only 20 first user from melt matrix

```{r}
#top 20

top_20_user <- melt_similar_user %>% 
  filter(value <1.0) %>% 
  arrange(desc(value)) %>% 
  top_n(20)
top_20_user

#least 20

least_20_user <- melt_similar_user %>% 
  filter(value <1.0) %>% 
  arrange(desc(value)) %>% 
  top_n(-20)
least_20_user
```


# The function geom_tile()[ggplot2 package] is used to visualize the correlation matrix :
```{r}
#top 20 user plot

ggplot(data = top_20_user, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

#least 20 user plot
ggplot(data = least_20_user, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```


